NoTitle

### 2017-06-12 Aplas17/sections/Formalization.tex

\subsection{Syntax} \haoyuan{TODO: syntactic sugar}

>>>>

\subsection{Syntax} \haoyuan{TODO: syntactic sugar; mention that path invocation subsumes
regular invocation; add explanation for interface check; use the examples to illustrate the
mbody algorithm in an intuitive way, and especially explain the two counter-examples that are
important to type soundness.}
